---
title: "Assignment 1"
---

# Assignment 1

My first assignment has two parts.

## (a)

[Securely store and share database credentials across projects with Data Connections \| Posit Cloud](https://www.youtube.com/watch?v=HFvJsWiQYbA&list=PL9HYL-VRX0oTOK4cpbCbRk15K2roEgzVW&index=3)

## (b)

### Differences

1.Indexing

Indexing in Python starts from 0.

```{python}
x=(1:4)
first_element=x[1] #output is 2 because first index is 0 we should use x[0] for first element of the list in python.
```

Indexing in R starts from 1.

```{r}
x <- c(1:4)
x #give us the list
first_element <- x[1]
first_element #when we try it in python output is going to be 2 because indexing starts from 0.
```

2.  Style

R use more simple programming language rather then python.

```{r}
y<-c(1,2,3,4,5)
square<-y^2 #using square root of the defined element give us the square of elements on the list.
square
```

```{python}
y = [1,2,3,4,5]
square = [x**2 for x in square] #we have to use for loop for calculate the square of the elements on the list. More complex than R.
```

3.  Syntax for Conditional Statements

Ifelse applies the condition to each element on the list without for loop.

```{r}
t <- c(1,2,3,4,5,6)
ifelse(t<4,t+1,0)

```

In python, we need for loop to apply the condition to each element on the list.

```{python}
t = [1,2,3,4,5,6]
new_list = [x + 1 if x < 4 else 0 for x in t]
```

```{r}

library(dslabs)

data("na_example")

print(na_example)


```


